Experiments on ANTS Algorithms Without Communication

### 2014-12-09 paper/draft.tex
added stuff for Lines uniform in k

\section{Lines Algorithm}
\label{lines}

@@

>>>>

\section{Lines Algorithms}
\label{lines}

@@

\subsection{Uniform in $k$}

Since we ultimately want to compare the algorithms discussed via simulations, we felt it was necessary to extend the lines algorithms with a variant uniform in $k$, which we could then compare with the uniform spiral algorithm and harmonic search.

The main idea for achieving uniformity in $k$ is borrowed from \cite{feinerman2012collaborative}: we start with a small guess for $k$, run the algorithm uniform in $D$ under this assumption, and then double out guess for $k$ and repeat. The implementation actually interleaves the increments of the $D$ and $k$ estimates, running one iteration of the non-uniform subroutine for each estimate.
